%-------------------------
% CV for Northeastern University Faculty in Latex
% Author : Zoe Kearney
% Based off of: https://www.overleaf.com/latex/templates/coles-resume-template/qhpynjcvjpcj
% Follows: https://theprofessorisin.com/2016/08/19/dr-karens-rules-of-the-academic-cv/
% License : MIT
%------------------------

% Document class and font size
\documentclass[a4paper,9pt]{extarticle}

% Packages
\usepackage[utf8]{inputenc} % For input encoding
\usepackage{geometry} % For page margins
\geometry{a4paper, margin=0.5in} % Set paper size and margins
\usepackage{titlesec} % For section title formatting
\usepackage{enumitem} % For itemized list formatting
\usepackage{xcolor}
\usepackage{changepage} % for adjustwidth environment
\usepackage[colorlinks=true, linkcolor=blue, urlcolor=blue]{hyperref}
\usepackage{fancyhdr} % <--- Added for footer
\usepackage{lipsum}

\definecolor{darkblue}{RGB}{0, 0, 238} % A deeper blue shade

\hypersetup{
    colorlinks=true,
    linkcolor=darkblue,
    urlcolor=darkblue
}

% Formatting
\setlist{noitemsep} % Removes item separation
\titleformat{\section}{\large\bfseries}{\thesection}{1em}{}[\titlerule] % Section title format
\titlespacing*{\section}{0pt}{\baselineskip}{\baselineskip} % Section title spacing

% custom url display
\newcommand{\shorturl}[2]{%
  \href{#1}{#2}%
}

% Footer setup
\usepackage{fancyhdr}
\setlength{\headheight}{14pt}
\setlength{\footskip}{12pt}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% larger footer text, slightly raised
\fancyfoot[L]{\raisebox{12pt}{\normalsize Tyler J. Wallett}}
\fancyfoot[R]{\raisebox{12pt}{\normalsize\thepage}}

% remove footer on first page
\fancypagestyle{firstpage}{
  \fancyhf{}
  \renewcommand{\headrulewidth}{0pt}
  \renewcommand{\footrulewidth}{0pt}
}


% Begin document
\begin{document}
\thispagestyle{firstpage}

% Header
\begin{center}
\textbf{\Huge Tyler J. Wallett }\\[3pt] % Name
Rockville, MD, USA | Relocating to Canada | Canadian Citizen | \href{https://github.com/twallett}{GitHub} | \href{https://www.twallett.com}{twallett.com} | \href{https://www.linkedin.com/in/twallett/}{LinkedIn} | +1 (301) 318-4569  % Contact info 
\end{center}

%------------------------
\section*{PROFESSIONAL SUMMARY}

\begin{adjustwidth}{0.4cm}{0cm}

Data Scientist with MS in Data Science and foundational expertise in statistical modeling, Python, and SQL-based analytics. Experience building predictive models, time-series forecasting, and ETL pipelines. Skilled in communicating technical findings to stakeholders and collaborating in cross-functional teams.

\end{adjustwidth}

\section*{EDUCATION}

\begin{itemize}[leftmargin=0.4cm, label={}]
    \item \textbf{Master of Science, Data Science} (GPA 3.9) \hfill May 2024 \\ 
    The George Washington University, Washington, D.C. \\ 
    Scholarship: Graduate Dean's Fellowship Merit-based.
\end{itemize}

\noindent
\begin{itemize}[leftmargin=0.4cm, label={}]
    \item \textbf{Bachelor of Business Administration, Finance} (GPA 3.7) \hfill June 2022 \\
    Bishop's University, Quebec, Canada. \\ 
    Scholarship: Ronald Crowley Merit-based. \\
    Relevant Coursework: Corporate Finance, Capital Markets, Investment Analysis, Financial Accounting.
\end{itemize}

%------------------------

\section*{PROFESSIONAL EXPERIENCE}

\begin{itemize}[leftmargin=0.4cm, label={}]
    \item \textbf{George Washington University} \hfill January 2025 - Present \\
    Data Science Instructional Technologist \& Professional Lecturer
    \vspace{-0.1cm}
    \begin{itemize}[leftmargin=0.3cm, label={}]
    \item \small{•} \normalsize{Collaborate with external partners (World Bank, research institutions) to deliver analytical solutions.}
    \item \small{•} \normalsize{Perform data analysis and communicate insights to stakeholders through presentations and technical documentation.}
    \item \small{•} \normalsize{Develop and deploy analytical workflows and cloud infrastructure (AWS) supporting 70+ users.}
    \item \small{•} \normalsize{Author technical curriculum and training materials for graduate-level data science education.}
    \end{itemize}
    Link: \href{https://twallett.com/courses/reinforcement-learning/}{Reinforcement Learning Course Website}
\end{itemize}

\noindent
\begin{itemize}[leftmargin=0.4cm, label={}]
    \item \textbf{eSource Capital} \hfill August 2024 - January 2025 \\
    Junior Data Scientist 
    \vspace{-0.1cm}
    \begin{itemize}[leftmargin=0.3cm, label={}]
\item \small{•} \normalsize{Built ML pipelines using Python and statistical methods for business intelligence analysis.}
    \item \small{•} \normalsize{Implemented data processing and semantic search systems using Python and cloud infrastructure.}
    \item \small{•} \normalsize{Deployed end-to-end analytical applications using Python and Streamlit for stakeholder consumption.}
    \end{itemize}
\end{itemize}

\noindent
\begin{itemize}[leftmargin=0.4cm, label={}]
    \item \textbf{The World Bank} \hfill March - May 2024 \\
    Data Science Consultant
    \vspace{-0.1cm}
    \begin{itemize}[leftmargin=0.3cm, label={}]
    \item \small{•} \normalsize{Delivered consulting services to design technical certification framework assessing competencies of 80+ personnel.}
    \item \small{•} \normalsize{Developed training materials and analytical exercises using Python, R, and statistical modeling techniques.}
    \item \small{•} \normalsize{Communicated technical recommendations to senior leadership through presentations and documentation.}
    \end{itemize}
\end{itemize}

\noindent
\begin{itemize}[leftmargin=0.4cm, label={}]
    \item \textbf{Base Operations} \hfill May - August 2023 \\
    Data Science Intern
    \vspace{-0.1cm}
    \begin{itemize}[leftmargin=0.3cm, label={}]
\item \small{•} \normalsize{Developed time-series forecasting models analyzing datasets to assess predictive performance.}
    \item \small{•} \normalsize{Built analytics dashboards using AWS and Python for operational insights and visualization.}
    \end{itemize}
\end{itemize}

%------------------------
\section*{DEPLOYED APPLICATIONS}

\begin{itemize}[leftmargin=0.4cm, label={}]
    \item \textbf{Production ML Pipelines} \hfill 2024 - Present \\
    Python, Scikit-Learn, Docker, FastAPI, Render
    \begin{itemize}[leftmargin=0.3cm, label={}]
    \item \small{•} \normalsize{Sales forecasting models using scikit-learn deployed via Docker and FastAPI for automated predictions.} 
    \item \small{•} \normalsize{Customer segmentation analysis (RFM) with end-to-end pipeline from data processing to deployment.}
    \end{itemize}
    Links: \href{https://twallett.com/sales-forecast}{Sales Forecast Demo} | \href{https://twallett.com/customer-segmentation}{Customer Segmentation Demo} 
\end{itemize}

%------------------------
\section*{TECHNICAL SKILLS}

\begin{itemize}[leftmargin=0.5cm, label={}]
\item \textbf{Programming \& Data Analysis:} Python, R, SQL, statistical modeling, data pipelines, Git/GitHub. \\

\item \textbf{Machine Learning:} scikit-learn, XGBoost, PyTorch, predictive modeling, time-series forecasting. \\

\item \textbf{Data Visualization:} Tableau, PowerBI, matplotlib, seaborn, plotly, Streamlit. \\

\item \textbf{Cloud \& Data Engineering:} AWS (EC2, S3), Docker, FastAPI, ETL, data pipelines, model deployment. \\

\item \textbf{Databases:} SQL, data manipulation, ETL processes. \\
\end{itemize}

\end{document}
