%-------------------------
% CV for Northeastern University Faculty in Latex
% Author : Zoe Kearney
% Based off of: https://www.overleaf.com/latex/templates/coles-resume-template/qhpynjcvjpcj
% Follows: https://theprofessorisin.com/2016/08/19/dr-karens-rules-of-the-academic-cv/
% License : MIT
%------------------------

% Document class and font size
\documentclass[a4paper,9pt]{extarticle}

% Packages
\usepackage[utf8]{inputenc} % For input encoding
\usepackage{geometry} % For page margins
\geometry{a4paper, margin=0.5in} % Set paper size and margins
\usepackage{titlesec} % For section title formatting
\usepackage{enumitem} % For itemized list formatting
\usepackage{xcolor}
\usepackage{changepage} % for adjustwidth environment
\usepackage[colorlinks=true, linkcolor=blue, urlcolor=blue]{hyperref}
\usepackage{fancyhdr} % <--- Added for footer
\usepackage{lipsum}

\definecolor{darkblue}{RGB}{0, 0, 238} % A deeper blue shade

\hypersetup{
    colorlinks=true,
    linkcolor=darkblue,
    urlcolor=darkblue
}

% Formatting
\setlist{noitemsep} % Removes item separation
\titleformat{\section}{\large\bfseries}{\thesection}{1em}{}[\titlerule] % Section title format
\titlespacing*{\section}{0pt}{\baselineskip}{\baselineskip} % Section title spacing

% custom url display
\newcommand{\shorturl}[2]{%
  \href{#1}{#2}%
}

% Footer setup
\usepackage{fancyhdr}
\setlength{\headheight}{14pt}
\setlength{\footskip}{12pt}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% larger footer text, slightly raised
\fancyfoot[L]{\raisebox{12pt}{\normalsize Tyler J. Wallett}}
\fancyfoot[R]{\raisebox{12pt}{\normalsize\thepage}}

% remove footer on first page
\fancypagestyle{firstpage}{
  \fancyhf{}
  \renewcommand{\headrulewidth}{0pt}
  \renewcommand{\footrulewidth}{0pt}
}


% Begin document
\begin{document}
\thispagestyle{firstpage}

% Header
\begin{center}
\textbf{\Huge Tyler J. Wallett }\\[3pt] % Name
Rockville, MD, USA | Relocating to Canada | Canadian Citizen | \href{https://github.com/twallett}{GitHub} | \href{https://www.twallett.com}{twallett.com} | \href{https://www.linkedin.com/in/twallett/}{LinkedIn} | +1 (301) 318-4569  % Contact info 
\end{center}

%------------------------
\section*{PROFESSIONAL SUMMARY}

\begin{adjustwidth}{0.4cm}{0cm}
Data Scientist specializing in financial analytics and risk detection with strong foundation in statistical modeling, machine learning, and large dataset analysis using Python and SQL. Experienced in developing predictive models and analytical solutions for business intelligence and risk assessment. Finance background (BBA) combined with advanced data science training (MS) enables effective translation of complex quantitative analyses into actionable insights. Proven ability to communicate technical findings to non-technical stakeholders and collaborate across diverse teams.
\end{adjustwidth}

%------------------------

\section*{EDUCATION}

\begin{itemize}[leftmargin=0.4cm, label={}]
    \item \textbf{Master of Science, Data Science} (GPA 3.9) \hfill May 2024 \\ 
    The George Washington University, Washington, D.C. \\ 
    Scholarship: Graduate Dean's Fellowship Merit-based.
\end{itemize}

\noindent
\begin{itemize}[leftmargin=0.4cm, label={}]
    \item \textbf{Bachelor of Business Administration, Finance} (GPA 3.7) \hfill June 2022 \\
    Bishop's University, Quebec, Canada. \\ 
    Scholarship: Ronald Crowley Merit-based. \\
    Relevant Coursework: Corporate Finance, Capital Markets, Investment Analysis, Financial Accounting.
\end{itemize}

%------------------------

\section*{PROFESSIONAL EXPERIENCE}

\begin{itemize}[leftmargin=0.4cm, label={}]
    \item \textbf{George Washington University} \hfill January 2025 - Present \\
    Data Science Instructional Technologist \& Professional Lecturer
    \vspace{-0.1cm}
    \begin{itemize}[leftmargin=0.3cm, label={}]
    \item \small{•} \normalsize{Collaborate with external partners (World Bank, research institutions) to deliver analytical solutions using Python and SQL.}
    \item \small{•} \normalsize{Perform quantitative analysis on large datasets and communicate complex findings to stakeholders through data visualizations.}
    \item \small{•} \normalsize{Develop and deploy analytical workflows and cloud infrastructure (AWS) supporting 70+ users.}
    \item \small{•} \normalsize{Author technical curriculum covering statistical modeling, feature development, and exploratory data analysis.}
    \end{itemize}
    Link: \href{https://twallett.com/courses/reinforcement-learning/}{Reinforcement Learning Course Website}
\end{itemize}

\noindent
\begin{itemize}[leftmargin=0.4cm, label={}]
    \item \textbf{eSource Capital} \hfill August 2024 - January 2025 \\
    Junior Data Scientist 
    \vspace{-0.1cm}
    \begin{itemize}[leftmargin=0.3cm, label={}]
    \item \small{•} \normalsize{Developed automated analytical systems using Python for pattern recognition and anomaly detection in business data.}
    \item \small{•} \normalsize{Built data processing pipelines for large-scale document analysis and intelligent data retrieval systems.}
    \item \small{•} \normalsize{Created end-to-end ML applications using Python, PyTorch for financial intelligence and risk assessment analysis.}
\end{itemize}
\end{itemize}

\noindent
\begin{itemize}[leftmargin=0.4cm, label={}]
    \item \textbf{The World Bank} \hfill March - May 2024 \\
    Data Science Consultant
    \vspace{-0.1cm}
    \begin{itemize}[leftmargin=0.3cm, label={}]
    \item \small{•} \normalsize{Delivered consulting services designing analytical frameworks for risk assessment of 80+ personnel using quantitative methods.}
    \item \small{•} \normalsize{Developed training materials incorporating Python, SQL, and statistical modeling for data analysis competency assessment.}
    \item \small{•} \normalsize{Presented technical recommendations and model performance findings to senior management through clear visualizations.}
    \end{itemize}
\end{itemize}

\noindent
\begin{itemize}[leftmargin=0.4cm, label={}]
    \item \textbf{Base Operations} \hfill May - August 2023 \\
    Data Science Intern
    \vspace{-0.1cm}
    \begin{itemize}[leftmargin=0.3cm, label={}]
    \item \small{•} \normalsize{Developed time-series forecasting models (ARIMA) for pattern detection and anomaly identification in large datasets.}
    \item \small{•} \normalsize{Built analytical dashboards using AWS S3, SQL databases, and Python visualization libraries for operational monitoring.}
    \end{itemize}
\end{itemize}

%------------------------
\section*{DEPLOYED APPLICATIONS}

\begin{itemize}[leftmargin=0.4cm, label={}]
    \item \textbf{Financial Analytics \& Risk Detection Models} \hfill 2024 - Present \\
    Python, Scikit-Learn, SQL, Docker, FastAPI
    \begin{itemize}[leftmargin=0.3cm, label={}]
    \item \small{•} \normalsize{Predictive modeling systems using scikit-learn for pattern recognition and threshold-based monitoring solutions.} 
    \item \small{•} \normalsize{Customer risk segmentation analysis with end-to-end pipeline from SQL data extraction to model deployment.}
    \end{itemize}
    Links: \href{https://twallett.com/sales-forecast}{Forecast Model Demo} | \href{https://twallett.com/customer-segmentation}{Risk Segmentation Demo} 
\end{itemize}

%------------------------
\section*{TECHNICAL SKILLS}

\begin{itemize}[leftmargin=0.5cm, label={}]
    \item \textbf{Programming \& Data Analysis:} Python (expert), SQL databases, statistical modeling, large dataset manipulation, Git/GitHub. \\
    
    \item \textbf{Data Visualization \& Reporting:} Python visualization (matplotlib, seaborn, plotly), Tableau, PowerBI, clear presentation of model performance to non-technical audiences. \\
    
    \item \textbf{Machine Learning \& Analytics:} Scikit-learn, supervised/unsupervised learning, time-series forecasting, exploratory data analysis, feature development, threshold optimization. \\
    
    \item \textbf{Advanced Analytics:} XGBoost, PyTorch, TensorFlow, anomaly detection, pattern recognition, predictive modeling. \\
    
    \item \textbf{Cloud \& Infrastructure:} AWS (EC2, S3), Docker, FastAPI, data pipelines, model deployment and maintenance.
\end{itemize}

% End document
\end{document}
