%-------------------------
% CV for Northeastern University Faculty in Latex
% Author : Zoe Kearney
% Based off of: https://www.overleaf.com/latex/templates/coles-resume-template/qhpynjcvjpcj
% Follows: https://theprofessorisin.com/2016/08/19/dr-karens-rules-of-the-academic-cv/
% License : MIT
%------------------------

% Document class and font size
\documentclass[a4paper,9pt]{extarticle}

% Packages
\usepackage[utf8]{inputenc} % For input encoding
\usepackage{geometry} % For page margins
\geometry{a4paper, margin=0.5in} % Set paper size and margins
\usepackage{titlesec} % For section title formatting
\usepackage{enumitem} % For itemized list formatting
\usepackage{xcolor}
\usepackage{changepage} % for adjustwidth environment
\usepackage[colorlinks=true, linkcolor=blue, urlcolor=blue]{hyperref}
\usepackage{fancyhdr} % <--- Added for footer
\usepackage{lipsum}

\definecolor{darkblue}{RGB}{0, 0, 238} % A deeper blue shade

\hypersetup{
    colorlinks=true,
    linkcolor=darkblue,
    urlcolor=darkblue
}

% Formatting
\setlist{noitemsep} % Removes item separation
\titleformat{\section}{\large\bfseries}{\thesection}{1em}{}[\titlerule] % Section title format
\titlespacing*{\section}{0pt}{\baselineskip}{\baselineskip} % Section title spacing

% custom url display
\newcommand{\shorturl}[2]{%
  \href{#1}{#2}%
}

% Footer setup
\usepackage{fancyhdr}
\setlength{\headheight}{14pt}
\setlength{\footskip}{12pt}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% larger footer text, slightly raised
\fancyfoot[L]{\raisebox{12pt}{\normalsize Tyler J. Wallett}}
\fancyfoot[R]{\raisebox{12pt}{\normalsize\thepage}}

% remove footer on first page
\fancypagestyle{firstpage}{
  \fancyhf{}
  \renewcommand{\headrulewidth}{0pt}
  \renewcommand{\footrulewidth}{0pt}
}


% Begin document
\begin{document}
\thispagestyle{firstpage}

% Header
\begin{center}
\textbf{\Huge Tyler J. Wallett }\\[3pt] % Name
Rockville, MD, USA | Relocating to Canada | Canadian Citizen | \href{https://github.com/twallett}{GitHub} | \href{https://www.twallett.com}{twallett.com} | \href{https://www.linkedin.com/in/twallett/}{LinkedIn} | +1 (301) 318-4569  % Contact info 
\end{center}

%------------------------
\section*{PROFESSIONAL SUMMARY}

\begin{adjustwidth}{0.4cm}{0cm}
Data Scientist with strong experience in business intelligence, data extraction, and stakeholder collaboration. Proven track record gathering analytical requirements, documenting business rules, and delivering data-driven insights to cross-functional teams. Combines technical expertise in SQL and Python with business acumen to translate complex data requirements into actionable solutions. Experienced communicating with diverse stakeholders and managing multiple initiatives in collaborative environments.
\end{adjustwidth}

%------------------------

\section*{EDUCATION}

\begin{itemize}[leftmargin=0.4cm, label={}]
    \item \textbf{Master of Science, Data Science} (GPA 3.9) \hfill May 2024 \\ 
    The George Washington University, Washington, D.C. \\ 
    Scholarship: Graduate Dean's Fellowship Merit-based.
\end{itemize}

\noindent
\begin{itemize}[leftmargin=0.4cm, label={}]
    \item \textbf{Bachelor of Business Administration, Finance} (GPA 3.7) \hfill June 2022 \\
    Bishop's University, Quebec, Canada. \\ 
    Scholarship: Ronald Crowley Merit-based. \\
    Relevant Coursework: Corporate Finance, Capital Markets, Investment Analysis, Financial Accounting.
\end{itemize}

%------------------------

\section*{PROFESSIONAL EXPERIENCE}

\begin{itemize}[leftmargin=0.4cm, label={}]
    \item \textbf{George Washington University} \hfill January 2025 - Present \\
    Data Science Instructional Technologist \& Professional Lecturer
    \vspace{-0.1cm}
    \begin{itemize}[leftmargin=0.3cm, label={}]
    \item \small{•} \normalsize{Collaborate with external partners (World Bank, research institutions) to gather analytical requirements and deliver data solutions.}
    \item \small{•} \normalsize{Perform data extraction and analysis using SQL and Python, communicating insights to stakeholders through presentations.}
    \item \small{•} \normalsize{Manage multiple analytical initiatives supporting 70+ users, ensuring data availability and accuracy.}
    \item \small{•} \normalsize{Document technical requirements and validate data mappings for analytical workflows and cloud infrastructure.}
    \end{itemize}
    Link: \href{https://twallett.com/courses/reinforcement-learning/}{Reinforcement Learning Course Website}
\end{itemize}

\noindent
\begin{itemize}[leftmargin=0.4cm, label={}]
    \item \textbf{eSource Capital} \hfill August 2024 - January 2025 \\
    Junior Data Scientist 
    \vspace{-0.1cm}
    \begin{itemize}[leftmargin=0.3cm, label={}]
    \item \small{•} \normalsize{Gathered business requirements and developed automated analytical report generation system using Python and SQL.}
    \item \small{•} \normalsize{Implemented data extraction and manipulation pipelines for business intelligence analysis.}
    \item \small{•} \normalsize{Collaborated with stakeholders to understand operational systems and validate data mappings for reporting needs.}
\end{itemize}
\end{itemize}

\noindent
\begin{itemize}[leftmargin=0.4cm, label={}]
    \item \textbf{The World Bank} \hfill March - May 2024 \\
    Data Science Consultant
    \vspace{-0.1cm}
    \begin{itemize}[leftmargin=0.3cm, label={}]
    \item \small{•} \normalsize{Delivered consulting services gathering business requirements and documenting analytical frameworks for 80+ personnel.}
    \item \small{•} \normalsize{Performed impact analysis and developed data extraction methodologies using SQL and Python.}
    \item \small{•} \normalsize{Managed stakeholder expectations and communicated technical recommendations to senior leadership.}
    \end{itemize}
\end{itemize}

\noindent
\begin{itemize}[leftmargin=0.4cm, label={}]
    \item \textbf{Base Operations} \hfill May - August 2023 \\
    Data Science Intern
    \vspace{-0.1cm}
    \begin{itemize}[leftmargin=0.3cm, label={}]
    \item \small{•} \normalsize{Collaborated with team members to gather BI requirements and perform data analysis on operational datasets.}
    \item \small{•} \normalsize{Built analytical dashboards using SQL data extraction and visualization tools for stakeholder reporting.}
    \end{itemize}
\end{itemize}

%------------------------
\section*{DEPLOYED APPLICATIONS}

\begin{itemize}[leftmargin=0.4cm, label={}]
    \item \textbf{Business Intelligence Analytics Platforms} \hfill 2024 - Present \\
    Python, SQL, Tableau, FastAPI, Docker
    \begin{itemize}[leftmargin=0.3cm, label={}]
    \item \small{•} \normalsize{Sales analytics and forecasting dashboard with data extraction pipelines supporting business reporting requirements.} 
    \item \small{•} \normalsize{Customer analytics platform with end-to-end data manipulation and visualization for stakeholder insights.}
    \end{itemize}
    Links: \href{https://twallett.com/sales-forecast}{Sales Forecast Demo} | \href{https://twallett.com/customer-segmentation}{Customer Segmentation Demo} 
\end{itemize}

%------------------------
\section*{TECHNICAL SKILLS}

\begin{itemize}[leftmargin=0.5cm, label={}]
    \item \textbf{Data Extraction \& Manipulation:} SQL, Python, data mining, ETL processes, statistical analysis. \\
    
    \item \textbf{Business Intelligence \& Visualization:} Tableau, Power BI, matplotlib, seaborn, plotly, analytical reporting. \\
    
    \item \textbf{Programming \& Analytics:} Python, R, scikit-learn, time-series analysis, predictive modeling, Git/GitHub. \\
    
    \item \textbf{Collaboration \& Documentation:} Stakeholder communication, requirements gathering, technical documentation, impact analysis. \\
    
    \item \textbf{Cloud \& Infrastructure:} AWS (EC2, S3), Docker, FastAPI, data pipelines, system integration.
\end{itemize}

% End document
\end{document}
